Report

### 2021-07-14 Rmd/report.Rmd
Add Rmd to workflow and relaxed_criteria branch

```{r prepare, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}

# load packages
library(papaja)
library(knitr)
library(tidyverse)
library(lubridate)
library(scales)
library(DiagrammeR)
library(janitor)
library(lme4)
library(broom.mixed)
library(gt)
library(patchwork)
library(htmltools)
library(wesanderson)
library(shiny)
library(here)

# create functions
logit_to_prob <- function(x) exp(x) / (1 + exp(x))

theme_custom <- function(){
	theme(
		panel.background = element_rect(fill = "transparent"),
		panel.grid = element_blank(),
		#panel.grid = element_line(colour = "grey", linetype = "dotted"),
		panel.border = element_rect(fill = "transparent", colour = "black"),
		text = element_text(colour = "black", size = 15),
		axis.text = element_text(colour = "black")
	)
}
theme_set(theme_custom())

# load data
gaze <- readRDS(here("Data", "Gaze", "d.rds"))
stimuli <- readRDS(here("Data", "Stimuli", "stimuli.rds"))
attrition <- readRDS(here("Results", "attrition.rds")) %>% 
	mutate(
		valid_gaze = valid_gaze_prime & valid_gaze_target,
		valid_status = case_when(
			!valid_vocab ~ "Invalid vocabulary",
			!valid_gaze ~ "Invalid gaze",
			!valid_participant ~ "Invalid participant",
			TRUE ~ "Valid"
		))
vocab <- readRDS(here("Data", "Vocabulary", "vocabulary.rds"))
participants <- readRDS(here("Data", "Participants", "participants.rds")) %>% 
	left_join(distinct(attrition, participant, age_group, valid_participant)) %>% 
	drop_na(participant) %>% 
	left_join(vocab) %>% 
	mutate(vocab_size_l1_center = scale(vocab_size_l1)[,1])
fit <- readRDS(here("Results", "fit.rds"))
fit_21_mon <- readRDS(here("Results", "fit_21_mon.rds"))
fit_21_mon_vocab <- readRDS(here("Results", "fit_21_mon_vocab.rds"))
fit_21_mon_vocab_pct <- readRDS(here("Results", "fit_21_mon_vocab_pct.rds"))
fit_21_mon_location <- readRDS(here("Results", "fit_21_mon_location.rds"))

@@

## Raw data

## Growth curve analysis {.tabset .tab-pills}

### Model details

@@

### Fixed effects

@@

### Random effects

@@

### Marginal means {.tabset .tab-pills}

#### Overall

@@

#### By vocabulary size

@@

@@

## Attrition {.tabset .tab-pills}

```{r participants_cdi, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
# plot participants
participants %>% 
	left_join(distinct(attrition, participant, valid_participant)) %>%
	left_join(vocab) %>% 
	drop_na(valid_participant) %>% 
	mutate(
		valid_status = case_when(
			valid_participant & !is.na(vocab_size_l1) ~ "Valid (+ CDI)",
			valid_participant & is.na(vocab_size_l1) ~ "Valid (no CDI)",
			!valid_participant ~ "Not valid"
		)
	) %>% 
	ggplot(aes(lp, fill = valid_status)) +
	facet_grid(location~age_group, scales = "free") +
	geom_bar(colour = NA) +
	geom_hline(yintercept = 24, linetype = "dashed") +
	scale_colour_brewer(palette = "Set1") +
	labs(x = "Group", y = "Sample size", fill = "Valid?") +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		axis.title.x = element_blank(),
		axis.text = element_text(size = 10),
		axis.title.y = element_text(angle = 90)
	) 
```

### By location

@@

### By group

@@

### By participant

@@

### By trial

@@

### By lexical frequency {.tabset .tab-pills}

#### Prime frequency

@@

#### Target frequency

@@

### By familiarity {.tabset .tab-pills}

#### Prime familiarity

@@

#### Target familiarity

@@

### By animacy {.tabset .tab-pills}

@@

@@

### By category {.tabset .tab-pills}

## 21 month-old monolinguals {.tabset .tab-pills}

### All data

@@

### Location

@@

### Vocabulary (median split)

```{r fixef_21_mon_vocab, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
main_effects <- confint.merMod(fit_21_mon_vocab, method = "Wald") %>% 
	as.data.frame() %>% 
	clean_names() %>% 
	drop_na(x2_5_percent) %>%
	rownames_to_column("term") %>% 
	right_join(clean_names(tidy(fit_21_mon_vocab, effects = "fixed"))) %>% 
	select(term, estimate, std_error, conf_lower = x2_5_percent, conf_upper = x97_5_percent,
		   statistic, df, p_value) %>% 
	gt() %>% 
	fmt_number(2:7) %>% 
	fmt_number(8, decimals = 3) %>% 
	cols_merge(starts_with("conf_"), pattern = "[{1}, {2}]") %>% 
	cols_label(
		term = md("**Predictor**"),
		estimate = md("**Estimate**"),
		std_error = md("**SE**"),
		conf_lower = md("**CI<sub>95%</sub>**"),
		statistic = md("***t***"),
		df = md("**df**"),
		p_value = md("***p***")
	) %>% 
	tab_style(
		style = list(
			cell_fill(color = "#ffc7a1")
		),
		locations = cells_body(
			columns = everything(),
			rows = p_value < 0.05
		)
	)
main_effects

@@

augment(fit_21_mon_vocab) %>% 
	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
	ggplot() +
	facet_wrap(~vocab_cat, ncol = 1) +
	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
				 fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
				 fun = mean, geom = "line", size = 1) +
	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
	geom_text(data = sample_size,
			  aes(x = -0.3, y = 0.95, label = paste0("N = ", n)),
			  show.legend = FALSE,
			  colour = "black", fill = "black") +
	labs(x = "Time bin (100 ms)", y = "Pr(Target fixation)",
		 colour = "Trial type", fill = "Trial type") +
	scale_y_continuous(limits = c(0, 1), labels = percent) + 
	scale_x_continuous(breaks = unique(gaze$ot1), labels = unique(gaze$time_bin)) +
	theme(
		axis.title.y = element_blank(),
		axis.text = element_text(size = 7),
		legend.position = "left"
	) +

	augment(fit_21_mon_vocab) %>% 
	mutate(elog_prob = logit_to_prob(elog)) %>% 
	group_by(participant, vocab_cat, trial_type) %>% 
	summarise(elog_prob = mean(elog_prob, na.rm = TRUE)) %>% 
	ggplot(aes(trial_type, elog_prob)) +
	facet_wrap(~vocab_cat, ncol = 1) +
	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
	geom_violin(aes( fill = trial_type, colour = trial_type), show.legend = FALSE) +
	geom_boxplot(width = 0.1, outlier.colour = NA, fill = "white", colour = "black") +
	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
	labs(x = "Trial type", y = "Pr(Target fixation)",
		 colour = "Trial type", fill = "Trial type") +
	scale_y_continuous(limits = c(0, 1), labels = percent) + 
	theme(
		axis.title = element_blank(),
		axis.ticks = element_blank(),
		axis.text.x = element_blank(),
		axis.text.y = element_blank()
	) +
	plot_layout(ncol = 2, guides = "collect", widths = c(0.5, 0.5)) &
	theme_custom() &
	theme(
		legend.position = "right",
		plot.caption = element_text(size = 10, hjust = 0),
		plot.caption.position = "plot"
	)
```

### Vocabulary (balanced)

```{r fixef_21_mon_vocab_pct, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}

main_effects <- confint.merMod(fit_21_mon_vocab_pct, method = "Wald") %>% 
	as.data.frame() %>% 
	clean_names() %>% 
	drop_na(x2_5_percent) %>%
	rownames_to_column("term") %>% 
	right_join(clean_names(tidy(fit_21_mon_vocab_pct, effects = "fixed"))) %>% 
	select(term, estimate, std_error, conf_lower = x2_5_percent, conf_upper = x97_5_percent,
		   statistic, df, p_value) %>% 
	gt() %>% 
	fmt_number(2:7) %>% 
	fmt_number(8, decimals = 3) %>% 
	cols_merge(starts_with("conf_"), pattern = "[{1}, {2}]") %>% 
	cols_label(
		term = md("**Predictor**"),
		estimate = md("**Estimate**"),
		std_error = md("**SE**"),
		conf_lower = md("**CI<sub>95%</sub>**"),
		statistic = md("***t***"),
		df = md("**df**"),
		p_value = md("***p***")
	) %>% 
	tab_style(
		style = list(
			cell_fill(color = "#ffc7a1")
		),
		locations = cells_body(
			columns = everything(),
			rows = p_value < 0.05
		)
	)
main_effects

@@

```{r gaze_time_21_mon_vocab_pct, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
# by vocab (balanced)
sample_size <- participants %>%
	drop_na(vocab_size_l1_center) %>% 
	filter(age_group=="21 months", lp=="Monolingual") %>% 
	arrange(location, desc(vocab_size_l1_center)) %>% 
	group_by(location) %>% 
	mutate(vocab_index = row_number()) %>% 
	ungroup() %>% 
	filter(
		((location=="Barcelona") & (vocab_index %in% 1:15)) |
			((location=="Oxford")) & (vocab_index %in% seq(
				max(vocab_index[location=="Oxford"])-15,
				max(vocab_index[location=="Oxford"])))
	) %>% 
	nrow() %>% 
	data.frame(n = .)

augment(fit_21_mon_vocab_pct) %>% 
	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
	ggplot() +
	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
	stat_summary(
		aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
		fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type), fun = mean, geom = "line", size = 1) +
	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
	geom_text(data = sample_size,
			  aes(x = -0.3, y = 0.95, label = paste0("n = ", n)),
			  colour = "black", fill = "black", show.legend = FALSE) +
	labs(x = "Time bin (100 ms)", y = "Pr(Target fixation)",
		 colour = "Trial type", fill = "Trial type") +
	scale_y_continuous(limits = c(0, 1), labels = percent) + 
	scale_x_continuous(breaks = unique(gaze$ot1), labels = unique(gaze$time_bin)) +
	theme(
		axis.title.y = element_blank(),
		axis.text = element_text(size = 7),
		legend.position = "left"
	) +

	augment(fit_21_mon_vocab_pct) %>% 
	mutate(elog_prob = logit_to_prob(elog)) %>% 
	group_by(participant, trial_type) %>% 
	summarise(elog_prob = mean(elog_prob, na.rm = TRUE)) %>% 
	ggplot(aes(trial_type, elog_prob)) +
	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
	geom_violin(aes(fill = trial_type, colour = trial_type), show.legend = FALSE) +
	geom_boxplot(width = 0.1, outlier.colour = NA) +
	labs(x = "Trial type", y = "Pr(Target fixation)",
		 colour = "Trial type", fill = "Trial type") +
	scale_y_continuous(limits = c(0, 1), labels = percent) + 
	theme(
		axis.title = element_blank(),
		axis.ticks = element_blank(),
		axis.text.x = element_blank(),
		axis.text.y = element_blank()
	) +
	plot_layout(ncol = 2, guides = "collect", widths = c(0.75, 0.25)) &
	theme_custom() &
	theme(
		legend.position = "right",
		plot.caption = element_text(size = 10, hjust = 0),
		plot.caption.position = "plot"
	)
```

>>>>

```{r params, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}

# load packages
library(targets)
library(papaja)
library(knitr)
library(tidyverse)
library(lubridate)
library(scales)
library(DiagrammeR)
library(janitor)
library(lme4)
library(broom.mixed)
library(gt)
library(patchwork)
library(htmltools)
library(wesanderson)
library(shiny)
library(here)

# load objects
tar_load(participants)
tar_load(stimuli)
tar_load(vocabulary)

# stringent version
tar_load(gaze)
tar_load(attrition)
tar_load(fit)
tar_load(fit_21_mon)
tar_load(fit_21_mon_vocab_split)
tar_load(fit_21_mon_vocab_balanced)
tar_load(fit_21_mon_location)

# relaxed version
tar_load(gaze_relaxed)
tar_load(attrition_relaxed)
tar_load(fit_relaxed)
tar_load(fit_21_mon_relaxed)
tar_load(fit_21_mon_vocab_split_relaxed)
tar_load(fit_21_mon_vocab_balanced_relaxed)
tar_load(fit_21_mon_location_relaxed)

theme_set(theme_custom()) # in utils.R
```

```{r prepare, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}

attrition <- attrition %>% 
	mutate(
		valid_gaze = valid_gaze_prime & valid_gaze_target,
		valid_status = case_when(
			!valid_vocab ~ "Invalid vocabulary",
			!valid_gaze ~ "Invalid gaze",
			!valid_participant ~ "Invalid participant",
			TRUE ~ "Valid"
		))

attrition_relaxed <- attrition_relaxed %>% 
	mutate(
		valid_gaze = valid_gaze_prime & valid_gaze_target,
		valid_status = case_when(
			!valid_vocab ~ "Invalid vocabulary",
			!valid_gaze ~ "Invalid gaze",
			!valid_participant ~ "Invalid participant",
			TRUE ~ "Valid"
		))

participants <- participants %>% 
	left_join(distinct(attrition, participant, age_group, valid_participant)) %>% 
	drop_na(participant) %>% 
	left_join(vocabulary) %>% 
	mutate(vocab_size_l1_center = scale(vocab_size_l1)[,1])

@@

## Stringent criteria  {.tabset .tab-pills}

### Growth curve analysis {.tabset .tab-pills}

#### Model details

@@

#### Fixed effects

@@

##### Random effects

@@

#### Marginal means {.tabset .tab-pills}

##### Overall

@@

##### By vocabulary size

@@

##### By location

@@

### Attrition {.tabset .tab-pills}

#### Summary

```{r participants_cdi, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
# plot participants
participants %>% 
	left_join(distinct(attrition, participant, valid_participant)) %>%
	left_join(vocabulary) %>% 
	drop_na(valid_participant) %>% 
	mutate(
		valid_status = case_when(
			valid_participant & !is.na(vocab_size_l1) ~ "Valid (+ CDI)",
			valid_participant & is.na(vocab_size_l1) ~ "Valid (no CDI)",
			!valid_participant ~ "Not valid"
		)
	) %>% 
	ggplot(aes(lp, fill = valid_status)) +
	facet_grid(location~age_group, scales = "free") +
	geom_bar(colour = NA) +
	geom_hline(yintercept = 24, linetype = "dashed") +
	scale_colour_brewer(palette = "Set1") +
	labs(x = "Group", y = "Sample size", fill = "Valid?") +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		axis.title.x = element_blank(),
		axis.text = element_text(size = 10),
		axis.title.y = element_text(angle = 90)
	) 
```

@@

#### By group

@@

#### By participant

@@

#### By trial

@@

#### By lexical frequency {.tabset .tab-pills}

##### Prime frequency

@@

##### Target frequency

@@

#### By familiarity {.tabset .tab-pills}

##### Prime familiarity

@@

##### Target familiarity

@@

#### By animacy {.tabset .tab-pills}

@@

#### By category {.tabset .tab-pills}

@@

### Raw data

### 21 month-old monolinguals {.tabset .tab-pills}

#### All data

@@

#### Location

@@

#### Vocabulary (median split)

```{r fixef_21_mon_vocab_split, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
main_effects <- confint.merMod(fit_21_mon_vocab_split, method = "Wald") %>% 
	as.data.frame() %>% 
	clean_names() %>% 
	drop_na(x2_5_percent) %>%
	rownames_to_column("term") %>% 
	right_join(clean_names(tidy(fit_21_mon_vocab_split, effects = "fixed"))) %>% 
	select(term, estimate, std_error, conf_lower = x2_5_percent, conf_upper = x97_5_percent,
		   statistic, df, p_value) %>% 
	gt() %>% 
	fmt_number(2:7) %>% 
	fmt_number(8, decimals = 3) %>% 
	cols_merge(starts_with("conf_"), pattern = "[{1}, {2}]") %>% 
	cols_label(
		term = md("**Predictor**"),
		estimate = md("**Estimate**"),
		std_error = md("**SE**"),
		conf_lower = md("**CI<sub>95%</sub>**"),
		statistic = md("***t***"),
		df = md("**df**"),
		p_value = md("***p***")
	) %>% 
	tab_style(
		style = list(
			cell_fill(color = "#ffc7a1")
		),
		locations = cells_body(
			columns = everything(),
			rows = p_value < 0.05
		)
	)
main_effects

@@

augment(fit_21_mon_vocab_split) %>% 
	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
	ggplot() +
	facet_wrap(~vocab_cat, ncol = 1) +
	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
				 fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
				 fun = mean, geom = "line", size = 1) +
	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
	geom_text(data = sample_size,
			  aes(x = -0.3, y = 0.95, label = paste0("N = ", n)),
			  show.legend = FALSE,
			  colour = "black", fill = "black") +
	labs(x = "Time bin (100 ms)", y = "Pr(Target fixation)",
		 colour = "Trial type", fill = "Trial type") +
	scale_y_continuous(limits = c(0, 1), labels = percent) + 
	scale_x_continuous(breaks = unique(gaze$ot1), labels = unique(gaze$time_bin)) +
	theme(
		axis.title.y = element_blank(),
		axis.text = element_text(size = 7),
		legend.position = "left"
	) +

	augment(fit_21_mon_vocab_split) %>% 
	mutate(elog_prob = logit_to_prob(elog)) %>% 
	group_by(participant, vocab_cat, trial_type) %>% 
	summarise(elog_prob = mean(elog_prob, na.rm = TRUE)) %>% 
	ggplot(aes(trial_type, elog_prob)) +
	facet_wrap(~vocab_cat, ncol = 1) +
	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
	geom_violin(aes( fill = trial_type, colour = trial_type), show.legend = FALSE) +
	geom_boxplot(width = 0.1, outlier.colour = NA, fill = "white", colour = "black") +
	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
	labs(x = "Trial type", y = "Pr(Target fixation)",
		 colour = "Trial type", fill = "Trial type") +
	scale_y_continuous(limits = c(0, 1), labels = percent) + 
	theme(
		axis.title = element_blank(),
		axis.ticks = element_blank(),
		axis.text.x = element_blank(),
		axis.text.y = element_blank()
	) +
	plot_layout(ncol = 2, guides = "collect", widths = c(0.5, 0.5)) &
	theme_custom() &
	theme(
		legend.position = "right",
		plot.caption = element_text(size = 10, hjust = 0),
		plot.caption.position = "plot"
	)
```

#### Vocabulary (balanced)

```{r fixef_21_mon_vocab_balanced, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}

main_effects <- confint.merMod(fit_21_mon_vocab_balanced, method = "Wald") %>% 
	as.data.frame() %>% 
	clean_names() %>% 
	drop_na(x2_5_percent) %>%
	rownames_to_column("term") %>% 
	right_join(clean_names(tidy(fit_21_mon_vocab_balanced, effects = "fixed"))) %>% 
	select(term, estimate, std_error, conf_lower = x2_5_percent, conf_upper = x97_5_percent,
		   statistic, df, p_value) %>% 
	gt() %>% 
	fmt_number(2:7) %>% 
	fmt_number(8, decimals = 3) %>% 
	cols_merge(starts_with("conf_"), pattern = "[{1}, {2}]") %>% 
	cols_label(
		term = md("**Predictor**"),
		estimate = md("**Estimate**"),
		std_error = md("**SE**"),
		conf_lower = md("**CI<sub>95%</sub>**"),
		statistic = md("***t***"),
		df = md("**df**"),
		p_value = md("***p***")
	) %>% 
	tab_style(
		style = list(
			cell_fill(color = "#ffc7a1")
		),
		locations = cells_body(
			columns = everything(),
			rows = p_value < 0.05
		)
	)
main_effects

@@

```{r gaze_time_21_mon_vocab_balanced, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
# by vocabulary (balanced)
sample_size <- participants %>%
	drop_na(vocab_size_l1_center) %>% 
	filter(age_group=="21 months", lp=="Monolingual") %>% 
	arrange(location, desc(vocab_size_l1_center)) %>% 
	group_by(location) %>% 
	mutate(vocab_index = row_number()) %>% 
	ungroup() %>% 
	filter(
		((location=="Barcelona") & (vocab_index %in% 1:15)) |
			((location=="Oxford")) & (vocab_index %in% seq(
				max(vocab_index[location=="Oxford"])-15,
				max(vocab_index[location=="Oxford"])))
	) %>% 
	nrow() %>% 
	data.frame(n = .)

augment(fit_21_mon_vocab_balanced) %>% 
	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
	ggplot() +
	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
	stat_summary(
		aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
		fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type), fun = mean, geom = "line", size = 1) +
	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
	geom_text(data = sample_size,
			  aes(x = -0.3, y = 0.95, label = paste0("n = ", n)),
			  colour = "black", fill = "black", show.legend = FALSE) +
	labs(x = "Time bin (100 ms)", y = "Pr(Target fixation)",
		 colour = "Trial type", fill = "Trial type") +
	scale_y_continuous(limits = c(0, 1), labels = percent) + 
	scale_x_continuous(breaks = unique(gaze$ot1), labels = unique(gaze$time_bin)) +
	theme(
		axis.title.y = element_blank(),
		axis.text = element_text(size = 7),
		legend.position = "left"
	) +

	augment(fit_21_mon_vocab_balanced) %>% 
	mutate(elog_prob = logit_to_prob(elog)) %>% 
	group_by(participant, trial_type) %>% 
	summarise(elog_prob = mean(elog_prob, na.rm = TRUE)) %>% 
	ggplot(aes(trial_type, elog_prob)) +
	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
	geom_violin(aes(fill = trial_type, colour = trial_type), show.legend = FALSE) +
	geom_boxplot(width = 0.1, outlier.colour = NA) +
	labs(x = "Trial type", y = "Pr(Target fixation)",
		 colour = "Trial type", fill = "Trial type") +
	scale_y_continuous(limits = c(0, 1), labels = percent) + 
	theme(
		axis.title = element_blank(),
		axis.ticks = element_blank(),
		axis.text.x = element_blank(),
		axis.text.y = element_blank()
	) +
	plot_layout(ncol = 2, guides = "collect", widths = c(0.75, 0.25)) &
	theme_custom() &
	theme(
		legend.position = "right",
		plot.caption = element_text(size = 10, hjust = 0),
		plot.caption.position = "plot"
	)
```

## Relaxed criteria  {.tabset .tab-pills}

### Growth curve analysis {.tabset .tab-pills}

#### Model details

#### Fixed effects

```{r fixed_effects_table_relaxed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
main_effects <- confint.merMod(fit_relaxed, method = "Wald") %>% 
	as.data.frame() %>% 
	clean_names() %>% 
	drop_na(x2_5_percent) %>%
	rownames_to_column("term") %>% 
	right_join(clean_names(tidy(fit_relaxed, effects = "fixed"))) %>% 
	select(term, estimate, std_error, conf_lower = x2_5_percent, conf_upper = x97_5_percent,
		   statistic, df, p_value) %>% 
	gt() %>% 
	fmt_number(2:7) %>% 
	fmt_number(8, decimals = 3) %>% 
	cols_merge(starts_with("conf_"), pattern = "[{1}, {2}]") %>% 
	cols_label(
		term = md("**Predictor**"),
		estimate = md("**Estimate**"),
		std_error = md("**SE**"),
		conf_lower = md("**CI<sub>95%</sub>**"),
		statistic = md("***t***"),
		df = md("**df**"),
		p_value = md("***p***")
	) %>% 
	tab_style(
		style = list(
			cell_fill(color = "#ffc7a1")
		),
		locations = cells_body(
			columns = everything(),
			rows = p_value < 0.05
		)
	)

##### Random effects

```{r random_effects_participant_relaxed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}

VarCorr(fit_relaxed)$participant %>% 
	cov2cor() %>% 
	as.data.frame() %>% 
	rownames_to_column("term1") %>% 
	gt(rowname_col = "term1") %>% 
	fmt_number(columns = 2:9) %>% 
	data_color(
		columns = 2:9,
		colors = col_numeric(
			palette = RColorBrewer::brewer.pal(n = 9, name = "Oranges"),
			domain = c(-1, 1), alpha = 0.5
		)
	)

#### Marginal means {.tabset .tab-pills}

##### Overall

```{r gaze_time_relaxed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
sample_size <- participants %>% 
	filter(valid_participant) %>% 
	count(age_group, lp)

augment(fit_relaxed) %>% 
	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
	ggplot() +
	facet_grid(lp~age_group) +
	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
				 fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
				 fun = mean, geom = "line", size = 1) +
	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
	geom_text(data = sample_size,
			  aes(x = -0.3, y = 0.95, label = paste0("n = ", n)),
			  show.legend = FALSE,
			  colour = "black", fill = "black") +
	labs(x = "Time bin (100 ms)", y = "Prob. of target fixation",
		 colour = "Trial type", fill = "Trial type",
		 caption = "Marginal means of the multilevel model, plotted in separate panels for monolinguals and bilinguals, across age\ngroups. Sample sizes are indicated at the upper left corner in each panel. The first and last 300 ms in each trial\nwere trimmed before the analysis.") +
	scale_y_continuous(limits = c(0, 1), labels = percent) + 
	scale_x_continuous(breaks = unique(gaze_relaxed$ot1), labels = unique(gaze_relaxed$time_bin)) +
	theme_custom() +
	theme(
		legend.position = "top",
		axis.text = element_text(size = 7),
		plot.caption = element_text(size = 10, hjust = 0),
		plot.caption.position = "plot"
	) 
```

##### By vocabulary size

```{r gaze_time_vocab_lower_relaxed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
sample_size <- participants %>% 
	count(age_group, lp)

augment(fit_relaxed) %>% 
	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
	filter(vocab_size_l1_center <= median(.$vocab_size_l1_center)) %>% 
	ggplot(aes(x = ot1, y = .fitted_prob)) +
	facet_grid(lp~age_group) +
	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
	stat_summary(aes(y = .fitted_prob, colour = trial_type, fill = trial_type), fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
	stat_summary(aes(y = .fitted_prob, colour = trial_type, fill = trial_type), fun = mean, geom = "line", size = 1) +
	geom_text(data = sample_size,
			  aes(x = -0.3, y = 0.95, label = paste0("n = ", n)),
			  show.legend = FALSE,
			  colour = "black", fill = "black") +
	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
	labs(x = "Time bin (100 ms)", y = "Prob. of target fixation",
		 colour = "Trial type", fill = "Trial type",
		 title = "Vocabulary size <= median") +
	scale_y_continuous(limits = c(0, 1)) + 
	scale_x_continuous(breaks = unique(gaze_relaxed$ot1), labels = unique(gaze_relaxed$time_bin)) +
	theme(
		legend.position = "top",
		axis.text = element_text(size = 7)
	)
```

```{r gaze_time_vocab_upper_relaxed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
sample_size <- participants %>% 
	filter(vocab_size_l1_center > median(.$vocab_size_l1_center, na.rm = TRUE), valid_participant) %>% 
	count(age_group, lp)

augment(fit_relaxed) %>% 
	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
	filter(vocab_size_l1_center > median(.$vocab_size_l1_center)) %>% 
	ggplot(aes(x = ot1, y = .fitted_prob)) +
	facet_grid(lp~age_group) +
	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
	stat_summary(aes(y = .fitted_prob, colour = trial_type, fill = trial_type), fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
	stat_summary(aes(y = .fitted_prob, colour = trial_type, fill = trial_type), fun = mean, geom = "line", size = 1) +
	geom_text(data = sample_size,
			  aes(x = -0.3, y = 0.95, label = paste0("n = ", n)),
			  show.legend = FALSE,
			  colour = "black", fill = "black") +
	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
	labs(x = "Time bin (100 ms)", y = "Prob. of target fixation",
		 colour = "Trial type", fill = "Trial type",
		 title = "Vocabulary size > median") +
	scale_y_continuous(limits = c(0, 1)) + 
	scale_x_continuous(breaks = unique(gaze_relaxed$ot1), labels = unique(gaze_relaxed$time_bin)) +
	theme(
		legend.position = "top",
		axis.text = element_text(size = 7)
	)
```

##### By location

```{r gaze_time_location_barcelona_relaxed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
sample_size <- participants %>% 
	filter(location=="Barcelona", valid_participant) %>% 
	count(age_group, lp)

augment(fit_relaxed) %>% 
	left_join(distinct(participants, participant, location)) %>% 
	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
	filter(location=="Barcelona") %>% 
	ggplot(aes(x = ot1, y = .fitted_prob)) +
	facet_grid(lp~age_group) +
	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
	stat_summary(aes(y = .fitted_prob, colour = trial_type, fill = trial_type), fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
	stat_summary(aes(y = .fitted_prob, colour = trial_type, fill = trial_type), fun = mean, geom = "line", size = 1) +
	geom_text(data = sample_size,
			  aes(x = -0.3, y = 0.95, label = paste0("n = ", n)),
			  show.legend = FALSE,
			  colour = "black", fill = "black") +
	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
	labs(x = "Time bin (100 ms)", y = "Prob. of target fixation",
		 colour = "Trial type", fill = "Trial type",
		 title = "Barcelona") +
	scale_y_continuous(limits = c(0, 1)) + 
	scale_x_continuous(breaks = unique(gaze_relaxed$ot1), labels = unique(gaze_relaxed$time_bin)) +
	theme(
		legend.position = "top",
		axis.text = element_text(size = 7)
	)
```

```{r gaze_time_location_oxford_relaxed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
sample_size <- participants %>% 
	filter(location=="Oxford") %>% 
	count(age_group, lp)

augment(fit_relaxed) %>% 
	left_join(distinct(participants, participant, location)) %>% 
	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
	filter(location=="Oxford") %>% 
	ggplot(aes(x = ot1, y = .fitted_prob)) +
	facet_grid(lp~age_group) +
	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
	stat_summary(aes(y = .fitted_prob, colour = trial_type, fill = trial_type), fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
	stat_summary(aes(y = .fitted_prob, colour = trial_type, fill = trial_type), fun = mean, geom = "line", size = 1) +
	geom_text(data = sample_size,
			  aes(x = -0.3, y = 0.95, label = paste0("n = ", n)),
			  show.legend = FALSE,
			  colour = "black", fill = "black") +
	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
	labs(x = "Time bin (100 ms)", y = "Prob. of target fixation",
		 colour = "Trial type", fill = "Trial type",
		 title = "Oxford") +
	scale_y_continuous(limits = c(0, 1)) + 
	scale_x_continuous(breaks = unique(gaze_relaxed$ot1), labels = unique(gaze_relaxed$time_bin)) +
	theme(
		legend.position = "top",
		axis.text = element_text(size = 7)
	)
```

### Attrition {.tabset .tab-pills}

#### Summary
